---
title       : Historical baby name occurence finder
subtitle    : A Shiny app
author      : M.K. McGregor
job         : Developing Data Products
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : solarized_light      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

--- .segue .quote .dark

<q> How common is your given name? Is your planned baby name too common?</q>

<style>
.dark q {
  color: white;
}
</style>

--- .class #id

## A new Shiny app

We propose a new simple Shiny app to give this information.

We make use of the US Social Security Administration database of baby names from 1880-2014
- Social security numbers (SSN) first issued in 1936, but only required for people with an income
- As of 1986, all children require a SSN at birth
- Data for males and females



--- .class #id 

## Let's take a look at the dataset

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(babynames)
data(babynames)
```

```{r head and tail, comment=NA}
head(babynames,3)
tail(babynames,3)
```

- n: number of records with that name
- prop: proportion = n divided total number of applicants in that year


--- .class #id 

## An Example: "Gertrude"

```{r plot, comment=NA}
years <- babynames[which(babynames$name == "Gertrude"), "year"]
props <- 100*babynames[which(babynames$name == "Gertrude"), "prop"]
plot(years, props, xlab= "Year", ylab = "Percent of births (%)", type = "l", lwd=3, col="blue")
```


